---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summarizeData

<!-- badges: start -->
<!-- badges: end -->

The `summarize_data` R package is a utility that provides a convenient way to perform group-wise summarization of data frames based on specified grouping variables and summary statistics. It simplifies the process of creating grouped summaries by allowing you to specify grouping variables and summary expressions in a clear and concise manner.

## Installation

You can install the development version of summarizeData from [GitHub](https://github.com/stat545ubc-2023/assignment-b2-kokowaahmax) with:

```{r}
# devtools::install_github("stat545ubc-2023/assignment-b2-kokowaahmax")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(summarizeData)

## basic example code
data <- data.frame(
  Group1 = c("A", "A", "B", "B"),
  Group2 = c("X", "Y", "X", "Y"),
  Value1 = c(10, 15, 20, NA),
  Value2 = c(5, 8, 12, 18)
)

# Usage of the summarize_data function
result <- summarize_data(data, group_vars = c("Group1", "Group2"),
                        Mean_Value1 = mean(Value1, na.rm = TRUE),
                        Sum_Value2 = sum(Value2, na.rm = TRUE))

# View the resulting summary data frame
head(result)
```


